---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# netscanR

<!-- badges: start -->
[![R-CMD-check](https://github.com/stibu81/netscanR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/stibu81/netscanR/actions/workflows/R-CMD-check.yaml)
[![Codecov test
coverage](https://codecov.io/gh/stibu81/netscanR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/stibu81/netscanR?branch=main)
<!-- badges: end -->


## About

netscanR is an R package that allows you to scan your local network using
`arp-scan`. Output from `arp-scan` is parsed into a tibble that can be
analysed using R.


## Installation

You can install the development version of netscanR from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stibu81/netscanR")
```


## Setting up `arp-scan`

`arp-scan` must be installed in order for netscanR to work. You can check that
the command can be found by running

```{r}
library(netscanR)
find_arp_scan()
```

If `arp-scan` is not found, an empty string is returned. On Linux, you
can usually install `arp-scan` from the official package repositories.
For example, on Debian, Ubuntu and derivatives, you can run

``` bash
sudo apt install arp-scan
```

`arp-scan` should also run on any other Linux  distribution, macOS, FreeBDS
and others (see the
[arp-scan GitHub readme](https://github.com/royhills/arp-scan?tab=readme-ov-file#building-and-installing-from-source)),
and once it is installed, netscanR might be able to run. However, this has only
been tested on Ubuntu.

The version of `arp-scan` can be obtained from R using

```{r}
arp_scan_version()
```

If `arp-scan` is not found, the returned version is 0.

netscanR has only been tested with `arp-scan` version 1.9.7.


## Usage

Once `arp-scan` is installed, you can scan the local network from R using

```{r eval=FALSE}
run_arp_scan()
```
<!-- in order not to disclose any private information, the test data is used
here instead of an actual call of run_arp_scan() -->
```{r echo=FALSE}
netscanR:::parse_arp_scan(netscanR:::get_arp_scan_test_output())
```


